### 2011-11-19 doc/theses/vitasek/chapter-3-mip.tex
Thesis: merging Lydka round 1.

Given a graph $G = (V,E)$ with a weight function $w: V \rightarrow \mathbb{R}$, we introduce a binary variable $x_i$ for each vertex $v_i \in V$ and an inequality constraint $x_i + x_j \leq 1$ for each edge $e = (v_i, v_j) \in E$. Furthermore we introduce an objective function in form $\sum_{x_i} x_i w(v_i)$.

It is obvious that the objective function and all the constraints consitute a MIP instance, and that solving it finds the maximum weigthed IS in $G$.

@@

Recall that attribute mappings in this example are $C = \{M_{y}^{a}, M_{y}^{b}, M_{y}^{c}, M_{z}^{a}\}$. Corresponding vertices in the IS formulation will be $V = \{v_{y-a}, v_{y-b}, v_{y-c}, v_{z-a}\}$. Edges in the IS formulation will be the following.

\begin{eqnarray*}
(v_{y-a},v_{y-b}) \\
(v_{y-a},v_{y-c}) \\
(v_{y-b},v_{y-c}) \\
(v_{y-a},v_{z-a}) \\
\end{eqnarray*}

@@

The problem now is, recall, to solve the following.

\begin{eqnarray*}
\max_{x} z & = & \mathbf{c}^{\mathrm{T}}\mathbf{x} \\
s.t.\, A\mathbf{x} & \leqslant & \mathbf{b} \\
\end{eqnarray*}

In GLPK \textit{MathProg} language (see \cite{mathprog}), this translates to the following formulation.

@@

This construction heuristic will be called \heu{Glpk} from now on. It is basically a time-constrained run of GLPK. Recall that GLPK uses a the \textit{Branch \& Bound} algorithm that produces feasible solutions even before the optimum is found. Limiting the run time gives us the best solution found so far, which means this is a construction heuristic.

>>>>

Given a~graph $G = (V,E)$ with a~weight function $w: V \rightarrow \mathbb{R}$, we introduce a~binary variable $x_i$ for each vertex $v_i \in V$ and an~inequality constraint $x_i + x_j \leq 1$ for each edge $e = (v_i, v_j) \in E$. Furthermore we introduce an~objective function in~form $\sum_{x_i} x_i w(v_i)$.

It is obvious that the objective function and all the constraints consitute a~MIP instance, and that solving it finds the maximum weigthed IS in $G$.

@@

Recall that attribute mappings in this example are $C = \{M_{y}^{a}, M_{y}^{b}, M_{y}^{c}, M_{z}^{a}\}$. Corresponding vertices in the IS formulation will be $V = \{v_{y-a}, v_{y-b}, v_{y-c}, v_{z-a}\}$. Edges in the IS formulation will be the following ones:

\begin{eqnarray*}
(v_{y-a},v_{y-b}), \\
(v_{y-a},v_{y-c}), \\
(v_{y-b},v_{y-c}), \\
(v_{y-a},v_{z-a}). \\
\end{eqnarray*}

@@

The problem now is, recall, to solve the following:

\begin{eqnarray*}
\max_{x} z & = & \mathbf{c}^{\mathrm{T}}\mathbf{x} \\
s.t.\, A\mathbf{x} & \leqslant & \mathbf{b}. \\
\end{eqnarray*}

In GLPK \textit{MathProg} language \cite{mathprog}, this translates to the following.

@@

This construction heuristic will be called \heu{Glpk} from now on. It is basically a~time-constrained run of GLPK. Recall that GLPK uses a the \textit{Branch \& Bound} algorithm that produces feasible solutions even before the optimum is found. Limiting the run time gives us the best solution found so far, which means this is a construction heuristic.

### 2011-11-19 doc/theses/vitasek/chapter-4-2-experiments-results.tex
Thesis: merging Lydka round 1.

Our experimental set will contain 500 experimental configurations for each of these two GLPK versions. Every configuration will use \heu{Glpk} CH set to a time limit from 1 to 46 seconds with increments of 5, meaning 10 settings * 50 iterations = 500 configurations in total (see Algorithm \ref{listing-experiment-glpk-native-vs-cygwin-1}). There will be no improvement heuristic. The only data we gather in the GnuPlot file are the final qualities (weights). The data set used is \dataset{100-500} as the biggest one in sized test data.\\

@@

The experimental results are summarized in Table \ref{table-experiments-fidax-and-hungry} and are quite surprising. As trivial a heuristic \heu{Hungry} is, it is still able to improve the ID set found by \heu{FIDAX} by as much as almost 50\% (the last row, \dataset{100-1000}).

Table \ref{table-experiments-fidax-and-hungry-idsets} lists the \texttt{ID} attributes found in both cases for this most extreme input, \dataset{100-1000}. Note that the content of each cell means ``attribute \texttt{attr} in element \texttt{vertexXY} should be marked as \texttt{ID} attribute''.

@@

We will use all the official data sets, set the pool size to 10 where applicable, $\alpha$ and $\beta$ to 1. This experiment will consist of 50 iterations * 11 data sets * 6 CHs = 3300 experimental configurations. See the Algorithm \ref{listing-experiment-best-standalone-ch} for details. This time we are not interested in run times, only in qualities which we shall gather in a format for GnuPlot.\\

@@

This experimental set will contain 6 data sets * 50 iterations * 4 IHs = 1200 experimental configurations. Note that we are using only the most challenging data sets, as the combination of \heu{Glpk} as CH and any other IH is already an overkill for easier data sets.\\

@@

We can see effects of different IHs from this graph:
\begin{itemize}
	\item Every $(1 + 5k)$\textsuperscript{th} and $(3 + 5k)$\textsuperscript{th} step is a \heu{RandomRemove}, and each time this happens there is a rather sharp drop in quality
	\item Every $(2 + 5k)$\textsuperscript{th} step is a \heu{Mutation}, and there is a consistent increase in quality each time.
	\item Every $(4 + 5k)$\textsuperscript{th} step is a \heu{Crossover}, and each time it happens there is a consistent increase, yet smaller than with \heu{Mutation}.
	\item Every $5k$\textsuperscript{th} step is a \heu{RemoveWorst}, and as expected, this removes the worst solution not touching the best ones that decide the incumbent quality. The line thus stays flat every time it happens.
\end{itemize}

>>>>

Our experimental set will contain 500 experimental configurations for each of these two GLPK versions. Every configuration will use \heu{Glpk} CH set to a~time limit from 1 to 46 seconds with increments of 5, meaning 10 settings * 50 iterations = 500 configurations in total (see Algorithm \ref{listing-experiment-glpk-native-vs-cygwin-1}). There will be no improvement heuristic. The only data we gather in the GnuPlot file are the final qualities (weights). The data set used is \dataset{100-500} as the biggest one in sized test data.\\

@@

The experimental results are summarized in Table \ref{table-experiments-fidax-and-hungry} and are quite surprising. Bold cells mean that adding \heu{Hungry} helped achieve a better quality. However trivial \heu{Hungry} is, it is still able to improve the ID set found by \heu{FIDAX} by as much as almost 50\% (the last row, \dataset{100-1000}).

Table \ref{table-experiments-fidax-and-hungry-idsets} lists the \texttt{ID} attributes found in both cases for this most extreme input, \dataset{100-1000}. Note that the content of each cell means ``attribute \texttt{attr} in~element \texttt{vertexXY} should be marked as \texttt{ID} attribute''.

@@

We will use all the official data sets, set the pool size to 10 where applicable, $\alpha$ and $\beta$ to 1. This experiment will consist of 50 iterations * 11 data sets * 6 CHs = 3300 experimental configurations. See the Algorithm \ref{listing-experiment-best-standalone-ch} for details. This time we are not interested in run times, only in qualities which we shall gather in format for GnuPlot.\\

@@

This experimental set will contain 6 data sets * 50 iterations * 4 IHs = 1200 experimental configurations. Note that we are using only the most challenging data sets, as the combination of \heu{Glpk} as CH and any other IH is already an~overkill for easier data sets.\\

@@

We can see effects of different IHs from this graph:
\begin{itemize}
	\item Every $(1 + 5k)$\textsuperscript{th} and $(3 + 5k)$\textsuperscript{th} step is~a~\heu{RandomRemove}, and each time this happens there is~a~rather sharp drop in~quality.
	\item Every $(2 + 5k)$\textsuperscript{th} step is a~\heu{Mutation}, and there is~a~consistent increase in~quality each time.
	\item Every $(4 + 5k)$\textsuperscript{th} step is a~\heu{Crossover}, and each time it~happens there is~a~consistent increase, yet smaller than with \heu{Mutation}.
	\item Every $5k$\textsuperscript{th} step is~a~\heu{RemoveWorst}, and as~expected, this removes the worst solution not touching the best ones that decide the incumbent quality. The line thus stays flat every time it~happens.
\end{itemize}

### 2011-11-19 doc/theses/vitasek/chapter-5-future.tex
Thesis: ready to send to reviewers.
Thesis: merging Lydka round 1.

A straightforward extension granting the ability to handle more than one input XML file has already been suggested in \cite{fidax}. However, it wasn't implemented in this work either, so it still remains an obvious first choice of future work.\\

It is possible (and easy) to add more construction and improvement heuristics, as well as more metaheuristics in which the existing IHs are chained. A starting point is in Section \ref{section-appendix-iss-howto}.\\

As it was mentioned in Section \ref{section-mip-ihs}, the combination of \heu{Crossover}, \heu{Mutation} and \heu{RemoveWorst} can be seen as a sort of genetic programming. However some modifications would still be necessary to make it a real instance of genetic algorithm metaheuristic.

>>>>

A straightforward extension granting the ability to handle more than one input XML file has already been suggested in \cite{fidax}. However, it was not implemented in this work either, so it remains an obvious first choice of future work.\\

It is possible (and easy) to add more construction and improvement heuristics, as well as more metaheuristics using the existing IHs. A~starting point is in Section \ref{section-appendix-iss-howto}.\\

As it was mentioned in Section \ref{section-mip-ihs}, the combination of \heu{Crossover}, \heu{Mu\-ta\-tion} and \heu{RemoveWorst} can be seen as a sort of genetic programming. However some modifications would still be necessary to make it a real instance of genetic algorithm metaheuristic.

### 2011-11-19 doc/theses/vitasek/diplomka.tex
Thesis: merging Lydka round 1.

\newpage % ============================================================
%%% Strana s čestným prohlášením k diplomové práci
\vglue 0pt plus 1fill
\noindent
I declare that I carried out this master thesis independently, and only with the cited
sources, literature and other professional sources.

\medskip\noindent
I understand that my work relates to the rights and obligations under the Act No.
121/2000 Coll., the Copyright Act, as amended, in particular the fact that the Charles
University in Prague has the right to conclude a license agreement on the use of this
work as a school work pursuant to Section 60 paragraph 1 of the Copyright Act.

@@

Název práce: Odvozování integritních omezení v XML % TODO how to translate this correctly?

@@

Vedoucí diplomové práce: \mfadvisor{} % TODO does this have to be here?, Ka\-ted\-ra soft\-wa\-ro\-vé\-ho in\-že\-nýr\-ství

Abstrakt: Tato práce navazuje na dřívější pokusy odvodit (inferovat) schéma existujících XML dokumentů. Jelikož je odvozování \textit{struktury} již relativně dobře popsáno, soustředíme se na integritní omezení. Několik jich popisujeme, pozornost pak soustředíme na ID/\.IDREF/\.IDREFS atributy z DTD. Na bázi článku od Barbosa a Menelzon (2003) stavíme heuristický přístup k problému hledání optimální sady ID atributů, jeho funkčnost a vhodnost pak ověřujeme na škále experimentů.

@@

Supervisor: \mfadvisor{} % TODO does this have to be here?, Department of Software Engineering

Abstract: In this work we~expand upon the previous efforts to~extract (infer) schema information from existing XML documents. We find the~inference of \textit{structure} to~be~sufficiently researched and focus further on~\textit{integrity constraints}. After briefly introducing some of~them we turn our attention to~ID/\.IDREF/\.IDREFS attributes in~DTD. Building on~the~research by~Barbosa and Menelzon (2003) we~introduce a~heuristic approach to~the~problem of~finding optimal ID set. The approach is~evaluated and tuned in~a~wide range of~experiments.

>>>>

\newpage % ============================================================
%%% Strana s čestným prohlášením k diplomové práci
\vglue 0pt plus 1fill
\noindent
I declare that I~carried out this master thesis independently, and only with the~cited sources, literature and~other professional sources.

\medskip\noindent
I~understand that my~work relates to~the~rights and~obligations under the~Act No.~121/2000 Coll., the~Copyright Act, as~amended, in~particular the~fact that the~Charles University in~Prague has the~right to~conclude a~license agreement on~the~use of this work as~a~school work pursuant to~Section 60 paragraph 1 of~the~Copyright Act.

@@

Název práce: Odvozování integritních omezení v XML

@@

Vedoucí diplomové práce: \mfadvisor{}

Abstrakt: Tato práce navazuje na dřívější pokusy odvodit (inferovat) schéma existujících XML dokumentů. Jelikož je~odvozování \textit{struktury} již relativně dobře popsáno, soustředíme se~na~integritní omezení. Několik jich popisujeme, pozornost pak soustředíme na~ID/\.IDREF/\.IDREFS atributy z DTD. Na~bázi článku od~Barbosa a~Menelzon (2003) stavíme heuristický přístup k~problému hledání optimální sady ID atributů, jeho funkčnost a~vhodnost pak ověřujeme na~škále experimentů.

@@

Supervisor: \mfadvisor{}

Abstract: In this work we~expand upon the~previous efforts to~infer schema information from existing XML documents. We find the~inference of~\textit{structure} to~be~sufficiently researched and focus further on~\textit{integrity constraints}. After briefly introducing some of~them we turn our attention to~ID/\.IDREF/\.IDREFS attributes in~DTD. Building on~the~research by~Barbosa and Menelzon (2003) we~introduce a~heuristic approach to~the~problem of~finding optimal ID set. The~approach is~evaluated and tuned in~a~wide range of~experiments.
